%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Benjamin Majkut} \\ \vspace{1pt}
    \small 860-234-4864 $|$ \href{mailto:x@x.com}{\underline{bmajkut9@gmail.com}} $|$ 
    %\href{https://linkedin.com/in/ben-majkut}{\underline{linkedin.com/in/ben-majkut}} $|$
    \href{https://github.com/bmajkut9}{\underline{github.com/bmajkut9}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- Present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Big Y Foods, Inc.}{Aug. 2020 -- Present}
      {Big Y World Class Market}{Mansfield Center, CT}
      \resumeItemListStart
        \resumeItem{Served as a dedicated cashier and service clerk for four years, demonstrating a strong commitment to customer service excellence and operational efficiency in a fast-paced retail environment.}
        \resumeItem{Fostered positive interactions and built strong relationships with both customers and team members, contributing to a welcoming and customer-oriented store atmosphere.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Focal: Deployed Mobile App} $|$ \emph{Flutter, Dart, NoSQL database}}{Jan 2024 -- March 2024}
          \resumeItemListStart
            \resumeItem{Using Flutter, Dart, and UI/UX design principles, built a full stack mobile application to fulfill market need of a high quality meditation timer.}
            \resumeItem{Leveraged Hive NoSQL database to integrate user analytics, such as streaks, total minutes meditated, session counts, and a heatmap calendar, fostering user retention.}
            \resumeItem{Gained over 100 downloads across 34 countries within first two weeks of release, achieving international impact.}
            \resumeItem{Successfully managed code signing and passed reviews for production release on both the Apple App Store and Google Play Store, complying with all security guidelines and quality requirements.}
            \resumeItem{Interacted with real world users by responding to emails and reviews, enhancing community support.}
            \resumeItem{Independently conducted all phases of app development from conceptualization and design to testing and deployment, demonstrating proficiency in full lifecycle app development.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Paper Paradise: Website} $|$ \emph{Bootstrap, HTML/CSS, Python, Django, SQL}}{April 2024 -- June 2024}
          \resumeItemListStart
            \resumeItem{Developed a real-time stock trading simulation website with HTML/CSS and Bootstrap on the frontend and Django on the backend.}
            \resumeItem{Used Yahoo Finance API to generate current and historical market data, providing an authentic and educational investing experience.}
            \resumeItem{Built a complex finance aggregation model with SQL and Django ORM to store and update all investment transactions.}
            \resumeItem{Implemented a secure user authentication system leveraging Django's built-in capabilities, ensuring data privacy and user-specific transaction management.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{YouTube Song Sorter (In Alpha testing)} $|$ \emph{JavaScript, React, YouTube API}}{May 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Using React and YouTube API, co-created a desktop application that could access a users YouTube account and sort their liked music videos into a playlist}
            \resumeItem{Implemented OAuth 2.0, adhering to the YouTube API's security protocols}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Statistical Model Simulation} $|$ \emph{Python}}{November 2023}
          \resumeItemListStart
            \resumeItem{Using Python, built a statical model of the envelope matching problem for a statistics class}
            \resumeItem{Achieved 99.9\% accuracy with model, resulting in an A+ grade on the project}
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Frameworks}{: Python, Bootstrap, Bash, Dart, JavaScript, SQL, HTML/CSS, Flutter, Django, React} \\
     \textbf{Skills}{: Mobile development, Web development, UI/UX Design, Automation, Databases, Material-UI, Figma design, Command line, APIs, OAuth 2.0}
    }}
 \end{itemize}

 \section{Personal Hobbies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}{Investing, Meditation, Chess, Weight lifting, Running, Tennis, Watches, Reading} \\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}

